PANCHANGE_analysis

### 2020-10-09 PANCHANGE_analysis.Rmd
Dataset for retro sensitivity analsyes created. GAD and PHQ 9 retrospective regressions were added using the sensitivity dataset for these analyses.

@@

@@

>>>>

```{r subsample for retro sensitivity analysis}
dat.retro_sensitivity <- dat %>%
  filter(
    ((data_group_gad == "All prepandemic, baseline and retrospective data") |
      (data_group_phq == "All prepandemic, baseline and retrospective data") |
      (data_group_pcl == "All prepandemic, baseline and retrospective data") |
      (data_group_ocir == "All prepandemic, baseline and retrospective data")) &
      prepandemic_march_1_numeric == 1 # Exclude participants that signed up after the 1. March
  )

@@

# GAD retro: sensitivity
## Regression: Change scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r gad model0a diff_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model0a_estimates <- model0a.estimates(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(gad_retro_model0a_estimates)
gad_retro_model0a_estimates

# Regression diagnostic statistics
gad_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(gad_retro_model0a_reg_stats)
gad_retro_model0a_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r gad model0b diff_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model0b_estimates <- model0b.estimates(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(gad_retro_model0b_estimates)
gad_retro_model0b_estimates

# Regression diagnostic statistics
gad_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(gad_retro_model0b_reg_stats)
gad_retro_model0b_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a diff_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model1a_estimates <- model1a.estimates(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(gad_retro_model1a_estimates)
gad_retro_model1a_estimates

# Regression diagnostic statistics
gad_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(gad_retro_model1a_reg_stats)
gad_retro_model1a_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b diff_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model1b_estimates <- model1b.estimates(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(gad_retro_model1b_estimates)
gad_retro_model1b_estimates

# Regression diagnostic statistics
gad_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "gad.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(gad_retro_model1b_reg_stats)
gad_retro_model1b_reg_stats
```

## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r gad model0a sum_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(gad_retro_model0a_explan_estimates)
gad_retro_model0a_explan_estimates

# Regression diagnostic statistics
gad_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(gad_retro_model0a_explan_reg_stats)
gad_retro_model0a_explan_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r gad model0b sum_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(gad_retro_model0b_explan_estimates)
gad_retro_model0b_explan_estimates

# Regression diagnostic statistics
gad_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(gad_retro_model0b_explan_reg_stats)
gad_retro_model0b_explan_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1a sum_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(gad_retro_model1a_explan_estimates)
gad_retro_model1a_explan_estimates

# Regression diagnostic statistics
gad_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(gad_retro_model1a_explan_reg_stats)
gad_retro_model1a_explan_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r gad model1b sum_score retro (sensitivity analysis)}
# Regression coefficients
gad_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(gad_retro_model1b_explan_estimates)
gad_retro_model1b_explan_estimates

# Regression diagnostic statistics
gad_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "gad.sum_score_base",
                                                               explan_var = "gad.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(gad_retro_model1b_explan_reg_stats)
gad_retro_model1b_explan_reg_stats
```

@@

# PHQ retro: Sensitivity
## Regression: Change scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r phq model0a diff_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model0a_estimates <- model0a.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(phq_retro_model0a_estimates)
phq_retro_model0a_estimates

# Regression diagnostic statistics
phq_retro_model0a_reg_stats <- model0a.reg.stats(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(phq_retro_model0a_reg_stats)
phq_retro_model0a_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r phq model0b diff_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model0b_estimates <- model0b.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(phq_retro_model0b_estimates)
phq_retro_model0b_estimates

# Regression diagnostic statistics
phq_retro_model0b_reg_stats <- model0b.reg.stats(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(phq_retro_model0b_reg_stats)
phq_retro_model0b_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a diff_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model1a_estimates <- model1a.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(phq_retro_model1a_estimates)
phq_retro_model1a_estimates

# Regression diagnostic statistics
phq_retro_model1a_reg_stats <- model1a.reg.stats(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(phq_retro_model1a_reg_stats)
phq_retro_model1a_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b diff_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model1b_estimates <- model1b.estimates(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(phq_retro_model1b_estimates)
phq_retro_model1b_estimates

# Regression diagnostic statistics
phq_retro_model1b_reg_stats <- model1b.reg.stats(outcome = "phq.diff_score_base_retro",
                                                 data_set = "dat.retro_sensitivity")
kable(phq_retro_model1b_reg_stats)
phq_retro_model1b_reg_stats
```

## Regression: Absolute scores
### Model 0a: Disorder_hierarchical, Unadjusted
```{r phq model0a sum_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model0a_explan_estimates <- model0a.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(phq_retro_model0a_explan_estimates)
phq_retro_model0a_explan_estimates

# Regression diagnostic statistics
phq_retro_model0a_explan_reg_stats <- model0a.explan.reg.stats(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(phq_retro_model0a_explan_reg_stats)
phq_retro_model0a_explan_reg_stats
```

### Model 0b: Overlapping disorders, Unadjusted
```{r phq model0b sum_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model0b_explan_estimates <- model0b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(phq_retro_model0b_explan_estimates)
phq_retro_model0b_explan_estimates

# Regression diagnostic statistics
phq_retro_model0b_explan_reg_stats <- model0b.explan.reg.stats(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(phq_retro_model0b_explan_reg_stats)
phq_retro_model0b_explan_reg_stats
```

### Model 1a: Disorder hierarchical, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1a sum_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model1a_explan_estimates <- model1a.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(phq_retro_model1a_explan_estimates)
phq_retro_model1a_explan_estimates

# Regression diagnostic statistics
phq_retro_model1a_explan_reg_stats <- model1a.explan.reg.stats(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(phq_retro_model1a_explan_reg_stats)
phq_retro_model1a_explan_reg_stats
```

### Model 1b: Overlapping disorders, Adjusted
Model 0a + Gender_collapsed + age_category_collapsed + Ethnicity_collapsed + Time registration and baseline
```{r phq model1b sum_score retro (sensitivity analysis)}
# Regression coefficients
phq_retro_model1b_explan_estimates <- model1b.explan.estimates(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(phq_retro_model1b_explan_estimates)
phq_retro_model1b_explan_estimates

# Regression diagnostic statistics
phq_retro_model1b_explan_reg_stats <- model1b.explan.reg.stats(outcome = "phq.sum_score_base",
                                                               explan_var = "phq.sum_score_retro",
                                                               data_set = "dat.retro_sensitivity")
kable(phq_retro_model1b_explan_reg_stats)
phq_retro_model1b_explan_reg_stats
```
